Arrangement for DroneGo

### 2020-03-09 PAPER.tex
Updates from Overleaf

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
     \vspace{5pt}
     \textbf{Keywords}: Sea-level Rise, EDPs , 3D Bin-Packing, Factor Analysis.

@@

2. to analyze the risk of loss of the culture behind the EDPs.

3. to guarantee the human rights of the EDPs, we established the evaluation models to arrange EDPs’ migration properly and provides  reference objectively

@@

>>>>

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
     \vspace{5pt}
     \textbf{Keywords}: Sea-level Rise, EDPs , Migration Model, Factor Analysis.

@@

2. To analyze the risk of loss of the culture behind the EDPs.

3. To guarantee the human rights of the EDPs, we established the evaluation models to arrange EDPs’ migration properly and provides  reference objectively

@@

%9.1
\subsection{Strengths}

\textbf{The first model}: This paper roughly estimated the potential population of EDPs based on the prediction of sea-level rise. Meanwhile, we analyzed the risk of cultural loss of EDPs and established a series of models. On the basis of these models, we proposed sets of the proposed policy to deal with EDPs in terms of human rights and  preservation of unique island culture.

\textbf{Second model}: Although the EDPs in different situations, the Conprehensive Index can be used to provide the optimal solution for the host country. At the same time, the ability of the host country to accept EDPs is fully considered, so that EDPs can be well integrated into the host country and will not become a burden on the host country. The most important thing is to properly balance the human rights of the EDPs with the responsibilities of the host country.

%9.2
\subsection{Weaknesses}

\textbf{The first model}: Ignoring the elevation of an island country and using its area as an indicator of whether an island country is at risk, it will lead to inaccurate estimates of the potential EDPs population.

\textbf{The second model}: due to limited space and time, not enough factors were considered in the evaluation of LCI and IRI.In the subsequent use of the model, new influencing factors can be taken in to improve the model.
